---
title: "Maxent_Models_forloop"
output: html_document
date: "2025-03-26"
Authors: Cindy Hurtado, Siobhan Darlington
---

Corrected mapping code re-written as a forloop to generate distribution maps across all species

Recommendation: Incorporate additional environmental covariates such as elevation, aspect, roads? 
Assign environmental covariates specific to each species within the forloop.

```{r}
library(spocc)
library(spThin)
library(dismo)
library(sf)
library(ENMeval)
library(wallace)
library(mapview)
library(rnaturalearth)
```
Revised forloop that doesn't require pulling the same environmental data every single time.
```{r}
# Define file path
occs_path <- "C:/LocalR/SDM_mesocarnivores/data"
occs_path <- file.path(occs_path, "wallace_data_March252025.csv")

# Get a list of species occurrence data
userOccs_Cl <- occs_userOccs(
  txtPath = occs_path, 
  txtName = occs_file, 
  txtSep = ",", 
  txtDec = "."
)

# Define environmental variables
env_vars <- c('bio01', 'bio02', 'bio03', 'bio04', 'bio05', 'bio06', 'bio07', 'bio08', 
              'bio09', 'bio10', 'bio11', 'bio12', 'bio13', 'bio14', 'bio15', 'bio16', 
              'bio17', 'bio18', 'bio19')

# Environmental data for western BC
envs_west <- envs_worldclim(
  bcRes = 0.5,
  bcSel = env_vars, 
  mapCntr = c(-120.511, 53.347),  # Adjust for western BC
  doBrick = TRUE
)

# Environmental data for eastern BC
envs_east <- envs_worldclim(
  bcRes = 0.5,
  bcSel = env_vars, 
  mapCntr = c(-114.511, 53.347),  # Adjust for eastern BC
  doBrick = TRUE
)

# Merge environmental data
envs_Cl <- merge(envs_west, envs_east)

# Storage list for results
species_results <- list()

# Loop through all species
for (species in names(userOccs_Cl)) {
  message("Processing: ", species)  # Show progress

  # Extract cleaned occurrence data
  occs_Cl <- userOccs_Cl[[species]]$cleaned
  
  # Skip species with no cleaned data
  if (nrow(occs_Cl) == 0) next

  # Extract environmental values for occurrences
  occs_xy_Cl <- occs_Cl[, c('longitude', 'latitude')]
  occs_vals_Cl <- as.data.frame(raster::extract(envs_Cl, occs_xy_Cl, cellnumbers = TRUE))

  # Remove duplicated same cell values
  occs_Cl <- occs_Cl[!duplicated(occs_vals_Cl[, 1]), ]
  occs_vals_Cl <- occs_vals_Cl[!duplicated(occs_vals_Cl[, 1]), -1]

  # Remove records with NA environmental values
  occs_Cl <- occs_Cl[!(rowSums(is.na(occs_vals_Cl)) >= 1), ]
  occs_vals_Cl <- na.omit(occs_vals_Cl)

  # Combine occurrences with environmental values
  occs_Cl <- cbind(occs_Cl, occs_vals_Cl)

  # Load BC boundary (this will be the same for each species)
  bc_boundary <- ne_states(country = "Canada", returnclass = "sf") %>% 
    dplyr::filter(name == "British Columbia")

  # Mask environmental data (this step is the same for each species)
  bgMask_Cl <- penvs_bgMask(
    occs = occs_Cl,
    envs = envs_Cl,
    bgExt = bc_boundary
  )

  # Sample background points (this step is the same for each species)
  bgSample_Cl <- penvs_bgSample(
    occs = occs_Cl,
    bgMask = bgMask_Cl,
    bgPtsNum = 10000
  )

  # Partition occurrence data (this step is the same for each species)
  groups_Cl <- part_partitionOccs(
    occs = occs_Cl,
    bg = bgSample_Cl,
    method = "block",
    bgMask = bgMask_Cl,
    aggFact = 2
  )

  # Extract background environmental values
  bgEnvsVals_Cl <- as.data.frame(raster::extract(bgMask_Cl, bgSample_Cl))
  bgEnvsVals_Cl <- cbind(scientific_name = paste0("bg_", species), bgSample_Cl,
                         occID = NA, year = NA, institution_code = NA, country = NA,
                         state_province = NA, locality = NA, elevation = NA,
                         record_type = NA, bgEnvsVals_Cl)

  # Store results for this species
  species_results[[species]] <- list(
    occurrences = occs_Cl,
    background = bgEnvsVals_Cl,
    partitions = groups_Cl
  )
}

# Print summary of results
print(lapply(species_results, function(x) nrow(x$occurrences)))


```

## Exclude species with low sample sizes:
```{r}
# Create an empty dataframe to store results
species_sample_sizes <- data.frame(Species = character(), 
                                   OrigSampleSize = integer(), 
                                   CleanedSampleSize = integer(), 
                                   stringsAsFactors = FALSE)

# Loop through userOccs_Cl and extract sample sizes
for (species_name in names(userOccs_Cl)) {
  orig_df <- userOccs_Cl[[species_name]]$orig      # Access the original dataframe
  cleaned_df <- userOccs_Cl[[species_name]]$cleaned  # Access the cleaned dataframe
  
  orig_size <- nrow(orig_df)     # Count number of rows in orig
  cleaned_size <- nrow(cleaned_df)  # Count number of rows in cleaned
  
  # Append to results dataframe
  species_sample_sizes <- rbind(species_sample_sizes, 
                                data.frame(Species = species_name, 
                                           OrigSampleSize = orig_size, 
                                           CleanedSampleSize = cleaned_size))
}

# View the final dataframe
print(species_sample_sizes)

### Urocyon_cineroargenteus, Erethizon_dorsatum, Spilogale_gracilis =< cleaned 22 obs

## Also subset out the species that did run correctly, for this test run:

# List of species to exclude
exclude_species <- c("Urocyon_cinereoargenteus","Erethizon_dorsatum", "Spilogale_gracilis")
# 
# "Taxidea_taxus", "Lynx_rufus", "Vulpes_vulpes","Tamiasciurus_hudsonicus", "Lynx_canadensis", "Pekania_pennanti", "Glaucomys_sabrinus", "Mustela_erminea", "Tamiasciurus_hudsonicus", "Neogale_vison", "Martes_americana", "Canis_latrans"

# Filter out species
filtered_species <- setdiff(names(species_results), exclude_species)

```




#run through model forloop
```{r}
library(raster)

# Storage list for model results
species_models <- list()

# Loop through each species
for (species in names(species_results)[!(names(species_results) %in% exclude_species)]) {
  message("Processing: ", species)  # Show progress

  # Extract data for the species
  occs_Cl <- species_results[[species]]$occurrences
  bgEnvsVals_Cl <- species_results[[species]]$background
  groups_Cl <- species_results[[species]]$partitions

  # 🚨 Check if occurrence data exists
  if (is.null(occs_Cl) || nrow(occs_Cl) == 0) {
    message("⚠ Skipping ", species, " due to missing occurrences")
    next
  }

  # Load BC boundary (ensure it works)
  bc_boundary <- tryCatch(
    ne_states(country = "Canada", returnclass = "sf") %>% 
      dplyr::filter(name == "British Columbia"),
    error = function(e) NULL
  )

  if (is.null(bc_boundary)) {
    message("⚠ Skipping ", species, " because BC boundary could not be loaded")
    next
  }

  # 🚨 Check if environmental layers exist
  if (!exists("envs_Cl") || is.null(envs_Cl) || !is(envs_Cl, "RasterBrick")) {
    message("⚠ Skipping ", species, " due to missing environmental layers")
    next
  }

  # Generate background mask
  bgMask_Cl <- tryCatch(
    penvs_bgMask(
      occs = occs_Cl,
      envs = envs_Cl,
      bgExt = bc_boundary
    ),
    error = function(e) NULL
  )

  if (is.null(bgMask_Cl)) {
    message("⚠ Skipping ", species, " because bgMask_Cl is NULL")
    next
  }

  # Sample background points
  bgSample_Cl <- penvs_bgSample(
    occs = occs_Cl,
    bgMask = bgMask_Cl,
    bgPtsNum = 10000
  )

  # Check if background points exist
  if (is.null(bgSample_Cl) || nrow(bgSample_Cl) == 0) {
    message("⚠ Skipping ", species, " due to missing background points")
    next
  }

  # ✅ Run MaxEnt model
  model_Cl <- model_maxent(
    occs = occs_Cl,
    bg = bgEnvsVals_Cl,
    user.grp = groups_Cl, 
    bgMsk = bgMask_Cl,
    rms = c(1, 2), 
    rmsStep = 1,
    fcs = 'L',
    clampSel = FALSE,
    algMaxent = "maxnet",
    parallel = FALSE,
    numCores = 27
  )

  # Store model results
  species_models[[species]] <- model_Cl
}

# Print summary of models
print(lapply(species_models, class))

```


Forloop through mapping each species distribution
```{r}
# Load necessary libraries
library(leaflet)
library(webshot)
library(htmlwidgets)
library(raster)

# Ensure webshot is installed
# webshot::install_phantomjs()

# Create output directory if it doesn't exist
if (!dir.exists("species_maps")) {
  dir.create("species_maps")
}

# Loop through all species
for (species in names(species_models)) {
  message("Creating map for: ", species)  # Show progress

  # Retrieve model and environmental data
  occs_Cl <- species_results[[species]]$occurrences
  # bgMask_Cl <- species_results[[species]]$background
  model_Cl <- species_models[[species]]  # Use the model from previous for-loop


  # Select MaxEnt model safely
  m_Cl <- tryCatch(model_Cl@models[["fc.L_rm.1"]], error = function(e) NULL)

    # Get prediction for the species using the model
  predSel_Cl <- tryCatch(
    predictMaxnet(m_Cl, bgMask_Cl, type = "logistic", clamp = FALSE),
    error = function(e) NULL
  )
  

  # Get values of prediction (ensure valid raster before proceeding)
  mapPredVals_Cl <- tryCatch(getValues(predSel_Cl), error = function(e) NULL)
   
  # Define colors and legend  
  rasCols <- c("#2c7bb6", "#abd9e9", "#ffffbf", "#fdae61", "#d7191c")  # Blue to Red
  legendPal <- colorNumeric(rasCols, mapPredVals_Cl, na.color = 'transparent')  
  rasPal <- colorNumeric(rasCols, mapPredVals_Cl, na.color = 'transparent')

  # Define specific legend values (ensuring they match the prediction range)
  legendValues <- seq(min(mapPredVals_Cl, na.rm = TRUE), max(mapPredVals_Cl, na.rm = TRUE), length.out = 5)

  # Generate the map using leaflet
  m <- leaflet() %>%
    addProviderTiles(providers$Esri.WorldTopoMap)

  m2 <- m %>%
    leaflet::addLegend("bottomright", pal = legendPal,
                       title = "Predicted Suitability",
                       values = rev(legendValues),  
                       labFormat = labelFormat(
                         suffix = "",  
                         prefix = "",  
                         between = " - "  
                       )) %>%
    # Add occurrence data
    addCircleMarkers(data = occs_Cl, lat = ~latitude, lng = ~longitude,
                     radius = 5, color = 'red', fill = TRUE, fillColor = "red",
                     fillOpacity = 0.2, weight = 2, popup = ~species) %>% 
    ## Add model prediction
    addRasterImage(predSel_Cl, colors = rasPal, opacity = 0.9,
                   group = 'vis', layerId = 'mapPred', method = "ngb")

  # Save the map to an HTML file
  map_filename <- paste0("species_maps/", species, "_map.html")
  saveWidget(m2, map_filename, selfcontained = TRUE)

  # Optionally, view the map in the RStudio Viewer
  print(m2)
}


```

Export rasters in a forloop

```{r}
# Load necessary libraries
library(raster)
library(leaflet)

# Define the output directory for saving rasters
output_dir <- "C:/LocalR/SDM_mesocarnivores/Output_species_maps"
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# Loop through species results and create/export rasters
for (species in names(species_results)) {
  message("Generating raster for: ", species)

  # Retrieve occurrence, background, and partition data
  occs_Cl <- species_results[[species]]$occurrences
  bgEnvsVals_Cl <- species_results[[species]]$background
  groups_Cl <- species_results[[species]]$partitions

  # Skip if no occurrences exist
  if (nrow(occs_Cl) == 0) next

  # Train the MaxEnt model
  model_Cl <- model_maxent(
    occs = occs_Cl,
    bg = bgEnvsVals_Cl,
    user.grp = groups_Cl, 
    bgMsk = bgMask_Cl,
    rms = c(1, 2), 
    rmsStep = 1,
    fcs = 'L',
    clampSel = FALSE,
    algMaxent = "maxnet",
    parallel = FALSE,
    numCores = 27
  )

  # Extract model and predict suitability
  m_Cl <- model_Cl@models[["fc.L_rm.1"]]
  predSel_Cl <- predictMaxnet(m_Cl, bgMask_Cl, type = "logistic", clamp = FALSE)

  # Define file path for raster export
  raster_filename <- file.path(output_dir, paste0(species, "_suitability.tif"))

  # Save the raster to file
  writeRaster(predSel_Cl, filename = raster_filename, format = "GTiff", overwrite = TRUE)

  message("Saved raster: ", raster_filename)
}

message("All rasters exported successfully!")

```

